A Comparative Ecophysiological Survey of Lycophytes, Ferns, and Seed Plants

### 2019-02-28 manuscript/manuscript.Rmd
stats for elemeents

Overall, no differences where detected in stomatal densities between species growing open canopy and closed canopy habitats. Specifically, differences in stomatal densities were not detected for either fern nor angiosperms species between the two habitats. However, in both open and closed environments, ferns had significantly lower stomatal densities than analogous angiosperms () (Figure asdfs). In

Similarly, ferns displayed a significantly lower SPAD index, a measurement of chlorophyll concentration, in open canopy environments versus closed canopies. Angiosperms showed no significant difference across the light gradient. In open environments, ferns had significantly lower SPAD index values than corresponding angiosperms, while the reverse was true in closed canopy habitats, with ferns displaying significantly higher values than analogous angiosperms (Figure asdfkj).

>>>>

Overall, no differences where detected in stomatal densities between species growing open canopy and closed canopy habitats. Specifically, differences in stomatal densities were not detected for either fern nor angiosperms species between the two habitats. However, in both open and closed environments, ferns had significantly lower stomatal densities than analogous angiosperms (*P* < 0.001).

In closed canopy environments, no differenes in stomatal density were detected among species of ferns, angiosperms and lycophytes. Variation in stomatal denisty in the shade was largely due to individual species variation.
